\bf On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2024-11-21 Manuscript/manuscript.tex
did some writing for gamlss results section

@@

The estimated parameters of the GLMM model under the log link are shown in 
Table~\ref{tab:Gamma_parameters}, both excluding and including 2022 data.
Three models were considered, differing in their random effects: venue effect
only; heat effect only, and both venue and heat effects. Reported are the AIC
and estimated model parameters: the standard deviation
of the heat effect $\sigma_h$, the standard deviation of the venue
effect~$\sigma_v$, the intercept~$\alpha$, and the
square root of the dispersion parameter $\phi$. With or without 2022,
the GLMM with both venue and heat random effects was the best model as evidenced
by the AIC compared to the other models with only one random
effect.  When we exclude 2022 from the full model, we observe small but intriguing
discrepancies in the models. The standard deviation of the venue effect, 
$\sigma_v$, increases from 0.33 to 0.40 when 2022 is included, however, the
estimates of other parameters
remained relatively similar, such as the standard deviation of the heat effect
and the dispersion parameter.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics{GGDensity}
  \caption{The densities of the GG distribution with random effects for heat
  and venue (black), and without random effects (blue)}
  \label{fig:DensityPlot}
\end{figure}

Figure~\ref{fig:VenueEffects} further illustrates the venue effect from 1999 to
2023 based on the full GLMM both with and without 2022.  The temporal patterns
of the two sets of effects look very similar, except that the positive effects
estimated with 2022 included have higher magnitude than those estimated without
2022, which compensates the negative effect of the 2022 with a large magnitude.
Both plots agree to some extent with the pattern of the boxplots in
Figure~\ref{fig:Boxplot}. The mismatch is due to the heat effect, since the venue
effect only captures a smaller part of the variation than the heat effect as
evident from their standard deviations. It is possible to calculate the extremity
of the 2022 heat effect as we know that the mean of the heat effects is $0$,
the standard deviation is $0.42$ as given by Table~\ref{tab:Gamma_parameters},
and the estimate of the 2022 heat effect is $-0.93$. We find the tail probability
to be $0.0128$ indicating there is a low chance of observing a venue effect as
extreme as 2022.

>>>>

We considered many types of models from various continuous distribution families
before ultimately deciding on the Generalized Gamma model desrcribed in
Section~\ref{sec:gamlss}.  The residuals of the GG model were particularly
strong, as evidenced by Figure~\ref{fig:Residuals}.  We care especially about
the lower residuals as we are trying to estimate the probability of a low reaction
time.  While there are two outliers present in the residual plot, we accept that
this is relatively small in relation to the rest of the roughly 770 observations.

@@

The estimated parameters of the GLMM model under the log link are shown in 
Table~\ref{tab:Gamma_parameters}, both excluding and including 2022 data.
.  We report the AIC, the point estimates for $\mu$,
$\sigma$, and $\mu$, as well as the standard deviations of the venue and heat
effects: $\sigma_v$ and $\sigma_h$ respectively. When we exclude 2022 from the
full model, we observe small but intriguing discrepancies in the models. The
standard deviation of the venue effect, $\sigma_v$, increases from 0.0434 to
0.0576 when 2022 is included. This suggests that by including 2022 in the model,
there is more of a variation in venue effects.

@@

The uniqueness of 2022 is further demonstrated by Figure~\ref{fig:VenueEffects},
which shows the values of the venue random effects.  The temporal patterns
of the two sets of effects look very similar, except that the positive effects
estimated with 2022 included have higher magnitude than those estimated without
2022, which compensates the negative effect of the 2022 with a large magnitude.
Both plots agree to some extent with the pattern of the boxplots in
Figure~\ref{fig:Boxplot}. The mismatch is due to the heat effect, since the venue
effect only captures a smaller part of the variation than the heat effect as
evident from their standard deviations. It is possible to calculate the extremity
of the 2022 heat effect as we know that the mean of the heat effects is $0$,
the standard deviation is $0.42$ as given by Table~\ref{tab:Gamma_parameters},
and the estimate of the 2022 heat effect is $-0.93$. We find the tail probability
to be $0.0128$ indicating there is a low chance of observing a venue effect as
extreme as 2022.

\begin{figure}[tbp]
  \centering
  \includegraphics{GGDensity}
  \caption{The densities of the GG distribution with random effects for heat
  and venue (black), and without random effects (blue)}
  \label{fig:DensityPlot}
\end{figure}
\of{Not sure what to write about the density plot or how to fit it into the rest
of the section.}
